---
title: "How Bad is it really"
author: "Simon"
date: "1/9/2022"
output: github_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse,viridis,magrittr,RColorBrewer,cowplot)

knitr::opts_chunk$set(echo = TRUE)


# Blackrock?
Anlagesumme=45467144553
Streumunition_landminen=(0.52/100)*Anlagesumme
Atomwaffen=(0.5/100)*Anlagesumme
ZivileWaffen=(0.23/100)*Anlagesumme
Tabak=(0.62/100)*Anlagesumme
UN_GloablCompactViolation=(0.82/100)*Anlagesumme
Kohle=(0.11/100)*Anlagesumme
Ölsand=(0.24/100)*Anlagesumme

total=Streumunition_landminen+Atomwaffen+ZivileWaffen+Tabak+UN_GloablCompactViolation+Kohle+Ölsand
```

# About

In this document i explore how much the capital in one of the most popular MSCI world ETF is
Specificially i try to get some scale on Blackrocks' iShares Core MSCI World UCITS ETF. 
All information is taken form Blackrocks' [self disclosure](https://www.ishares.com/de/privatanleger/de/produkte/251882/ishares-msci-world-ucits-etf-acc-fund).
According to their website the iShares Core MSCI World UCITS has a capital of 47055706319,35 USD. 0.52% is invested in companies, that produce controversial weapons such as landmines or fragmentation grenades. while 0.52% does not sound like much it still amounts to `r round(Streumunition_landminen/10^9,3)` Billion USD. 0.50% are invested in nuclear weapons, `r 47055706319*0.005` USD. In total, the iShares Core MSCI World UCITS invests `r round(total/10^9,3)` Billion dollars in morally repugnant buisnesses. 


## Compare the MSCI world to Country GDP.

As i have no idea how much 47055706319 USD really is, we need a scale to comprehend these numbers, so i downloaded 
a dataset that contains [all contries' GDPs](https://data.worldbank.org/indicator/NY.GDP.MKTP.CD) and visually relate 
them the capital of the ETF. This file contains summaries as well, i clean them.

```{r pressure, echo=FALSE}
numextract <- function(string){ 
  str_extract(string, "\\-*\\d+\\.*\\d*")
} 
#opearater that returns true for any value that is not in a list
`%notin%` <- Negate(`%in%`)


GDP<-read.csv("GDPDATA.csv",skip = 4)%>%
  pivot_longer(cols=starts_with("X"),names_to = "Year",values_to = "GDP")%>%
  mutate(GDP=GDP/10^9,Year=as.numeric(numextract(Year)))#show in Billion. (Milliarden)
#There are a couple of wierd cases or summaries in there. Filter them out.

Odd_Cases=read.csv(file ="odd_ones.csv",header=T)#%>%filter(Odd_Codes!="LIC" & Odd_Codes!="HPC")
  #leave low income in

GDP%<>%filter(Country.Code %notin% Odd_Cases$Odd_Codes)
```

```{r}

Code_breaks=GDP$Country.Code%>%unique()
Colors=rep("grey",length(Code_breaks))
Size=rep(0.5,length(Code_breaks))
Alphas=rep(0.1,length(Code_breaks))

ColourContries=c("ARE","BFA","COG","CHE","DEU","GRC","IRQ","YEM")%>%sort()#which Contries do you want to highlight?
  
Highlights=brewer.pal(n=length(ColourContries),name="Spectral")
Colors[which(Code_breaks %in% ColourContries)]=Highlights

legend<-cowplot::get_legend(ggplot(data.frame(ColourContries),aes(x=ColourContries,fill=ColourContries))+
  geom_bar()+scale_fill_manual(name="GPD of",breaks=ColourContries,values=Highlights)
)

#make highlight vectors
Colors[which(Code_breaks %in% ColourContries)]=Highlights
Size[which(Code_breaks %in% ColourContries)]=0.8
Alphas[which(Code_breaks %in% ColourContries)]=1

GDPPlot<-GDP%>%filter(Year>1990)%>%
  ggplot(aes(x=Year,y=GDP))+
  geom_line(aes(color=Country.Code,alpha=Country.Code,size=Country.Code))+
  geom_hline(yintercept=Anlagesumme/10^9,color="blue")+
  geom_hline(yintercept=total/10^9,color="red")+
  scale_y_log10("Country GDP in Billion [logscale]")+
  scale_color_manual(breaks=Code_breaks,values = Colors)+
  scale_size_manual(breaks=Code_breaks,values = Size)+
  scale_alpha_manual(breaks=Code_breaks,values = Alphas)+
  theme_bw()+
  theme(legend.position="none")

```


```{r fig.height=3,fig.width=4}
plot_grid(GDPPlot,legend, rel_widths = c(1,0.3))
```
```{r}
GDP%>%filter(Year>1990)%>%group_by(Country.Code)%>%
  summarize(mGDP=mean(GDP,na.rm=T),
            sem=sd(GDP,na.rm=T)/sqrt(n()))%>%filter(!is.na(mGDP))->GDP2

    #arrange(mGDP)%>%
GDP2$Country.Code=factor(GDP2$Country.Code,levels=GDP2$Country.Code[order(GDP2$mGDP)])

```

# 

```{r fig.width=5,fig.height=10}
figure<-GDP2%>%
  ggplot(aes(y=Country.Code,x=mGDP))+
  geom_point()+
  geom_errorbarh(aes(xmin=mGDP-sem,xmax=mGDP+sem))+
  scale_x_log10(name="Country GDP average since 1990 in Billion (sem) [logscale]")+
  geom_vline(xintercept=Anlagesumme/10^9,color="blue")+
  geom_vline(xintercept=total/10^9,color="red")+
  annotate(geom = "text", x = Anlagesumme/10^9-37, y=220, label="Total sum invested",color="blue")+
  annotate(geom = "text", x = (total/10^9)-1.25,y=200, label="Sum invested in morally\nrepugnant buisnesses",color="red")+
  ggtitle("Your favorite Blackrock ETFcompared to Country GDP",subtitle="iShares Core MSCI World UCITS ETF")+
  theme_cowplot(14)+
  theme(axis.text.y=element_text(size=4))
#ggsave("fun.png",width = 7,height=10)
```

# A nicer y axis
```{r}
GDP2%>%arrange(mGDP)%>%
  mutate(percent=percent_rank(mGDP))%>%
  ggplot(aes(y=percent,x=mGDP))+
  geom_point()+
  geom_errorbarh(aes(xmin=mGDP-sem,xmax=mGDP+sem))+
  scale_x_log10(name="Country GDP average since 1990 in Billion (sem) [logscale]")+
  scale_y_continuous(name="Percent Rank Countries")+
  geom_vline(xintercept=Anlagesumme/10^9,color="blue")+
  geom_vline(xintercept=total/10^9,color="red")+
  annotate(geom = "text", x = Anlagesumme/10^9-37, y=0.8, label="Total sum invested",color="blue")+
  annotate(geom = "text", x = (total/10^9)-1.25,y=0.8, label="Sum invested in morally\nrepugnant buisnesses",color="red")+
  ggtitle("Your favorite Blackrock ETFcompared to Country GDP",subtitle="iShares Core MSCI World UCITS ETF")+
  theme_minimal(14)
  #theme(axis.text.y=element_text(siz))
```